Two-Phase Commit Using Blockchain

### 2022-06-04 paper/paper.tex
Fixed two issues.

\section{Implementation}
In this section we first describe the implementation of our overall system. Then, we illustrate the implementation of individual components. The source code of our implementation is available at licensed under GNU Lesser General Public License. Our implementation depends on the following libraries: truffle \cite{github_truffle}, gganacheanache \cite{github_ganache}, sqlite3 \cite{github_sqlite3}, grpc \cite{github_grpc}, web3 \cite{github_web3}, abseil-cpp \cite{github_absl}, rule\_nodejs \cite{github_rulejs}, gflags \cite{github_gflags}, glog \cite{github_glog}, openssl \cite{github_openssl}, threadpool \cite{Shoshany2021_ThreadPool}, lmdb \cite{github_lmdb}, and lmdbxx \cite{github_lmdbxx}.

>>>>

\section{Implementation}
In this section we first describe the implementation of our overall system. Then, we illustrate the implementation of individual components. The source code of our implementation is available at licensed under GNU Lesser General Public License. Our implementation depends on the following libraries: truffle \cite{github_truffle}, ganache \cite{github_ganache}, sqlite3 \cite{github_sqlite3}, grpc \cite{github_grpc}, web3 \cite{github_web3}, abseil-cpp \cite{github_absl}, rule\_nodejs \cite{github_rulejs}, gflags \cite{github_gflags}, glog \cite{github_glog}, openssl \cite{github_openssl}, threadpool \cite{Shoshany2021_ThreadPool}, lmdb \cite{github_lmdb}, and lmdbxx \cite{github_lmdbxx}.
